\propertitle

### 2019-12-02 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-01T17:40:51+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The limitations of the proposed approach can be appraised by examining the
assumptions and approximations on which it rests. Its assumptions and
approximations become clear within a full-fledged probabilistic approach to
our inference problem, at least qualitatively sketched.

The first and most important assumption of this kind of maximum-entropy
application in neuroscience is that the order of the time bins has no
relevance; or equivalently that the frequencies of the activity during a
recording are informationally sufficient. Note that the maximum-entropy
method in statistical physics is meant to be used not with this assumption,
but with averages across \emph{repetitions} of the same experiment: its
constraints represent macroscopically \emph{reproducible} quantities and
kinematics, even in non-equilibrium
\citep{jaynes1957,guntonetal1983,tikochinskyetal1984,grandy1988,berryetal1988,deroecketal2005_r2006,touchette2009}.

@@

Both assumptions above make sense as hypotheses for judging the
informational relevance of correlations of some order, as in
\sect~\ref{sec:marginalization}, to be compared with hypotheses about more
realistic time dependences and clustering.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-02T10:04:27+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The limitations of approach here proposed can be appraised by examining the
assumptions and approximations on which it rests. Its assumptions and
approximations become clear within a full-fledged probabilistic inference
problem, which we sketch qualitatively.

The first and most important assumption of this kind of maximum-entropy
application in neuroscience can be expressed in three equivalent ways:
\begin{enumerate*}[(\roman*)]
\item the order of the time bins has no relevance; \item the frequencies of
  the activity during a recording are informationally sufficient for
  inferences about unrecorded times; \item our degree of belief about the
  sequence of activities is invariant under permutations of the time bins,
  that is, exchangeable \citep[\chap~4]{bernardoetal1994_r2000}{dawid2013}.
\end{enumerate*}
Equating time averages and expectations, \eqn~\eqref{eq:final_constraint},
would not make sense without this assumption. Its mathematical consequence
\citep{definetti1930,hewittetal1955} is that the probability of observing a
frequency distribution $(\yFF_{\yA})$ in $T$ time bins is given by a
mixture of terms
\begin{equation}
  \label{eq:mixture_from_definetti}
  \exp[-T\;\sh(\yF;\ynu)] \quad
  \text{with weights }q(\ynu),
\end{equation}
where $\ynu\defd (\nu_{\yA})$ represents the long-run frequency
distribution for the activity. % Other maximum-entropy models are also used
% in neuroscience, such as kinetic Ising models
% \cite{kawasaki1972,mezardetal2011,battistinetal2015}, based on the slightly
% less drastic assumption of invariance under permutations of sequences
% having the same starting state and the same transition counts
% \citep{diaconisetal1980c,geetal2012}.
Note that the maximum-entropy method in statistical physics is meant to be
used not with this assumption, but with averages across \emph{repetitions}
of the same experiment: its constraints represent macroscopically
\emph{reproducible} quantities and kinematics, even in non-equilibrium
\citep{jaynes1957,guntonetal1983,tikochinskyetal1984,grandy1988,berryetal1988,deroecketal2005_r2006,touchette2009}.

@@

Both assumptions above make sense as toy hypotheses for judging the
informational relevance of correlations of some order, as in
\sect~\ref{sec:marginalization}, to be compared with hypotheses about more
realistic time dependences and clustering.
